A Recipe for Scavenging \textcolor{blue}{in Vertebrates} - the natural history of a behaviour

### 2016-07-29 response_letter.tex

We would like to thank the editor, subject editor and reviewers for their comments. By bringing attention to elements of the manuscript that require more careful communication we believe that you have helped us to significantly improve our manuscript. In this submission we have clarified these areas and added a body of work to bolster the conclusions drawn from our work. Please see below where we consider each of your points in turn.
For improved clarity in this document and in the manuscript, we have highlighted our responses in \textcolor{blue}{blue}.

\section{Recommendation by the Subject Editor (anonymous):}
Three experienced reviews have evaluated your manuscript.
Two of them are extremely critical of several aspects related to to the general handcraft and novelly of the review.
The third reviewer is more positive, while making substantial recommendations for improvement of the manuscript.
Should you be able to address all of the reviewers comments in a much revised version of the manuscript I would happy to reconsider the manuscript for consideration in Ecography and the E4 Award.
This is not a provisional acceptance, since the manuscript would need to be revised again.

\smallskip

\textcolor{blue}{As we note below, we feel our earlier manuscript did not capture the hierarchy we had in mind.
This updated version is more explicit in terms of the structure where we now highlight the sections and subsections.
Regarding the novelty of our manuscript, we have changed our introduction which was regarded as too similar to deValult et al. (2003) and argue our case for what we consider inevitable overlap with Beasley et al. (2015).}

@@

\section{Reviewer: 1}
This paper attempts to synthesize literature on traits that enable scavenging behavior in extant and extinct vertebrates.
The paper is mostly well written, and most (but not all) pertinent literature sources are included.
I do worry about the lack of novelty of the manuscript, and what I perceived as haphazard organization. Here are some specific issues that should be addressed in my opinion:

\begin{enumerate}
\item{Abstract: Scavenging can be difficult to observe, but probably no more so than predation.
Also, using experimental carcasses, scavenging is actually quite easy to observe.}

\textcolor{blue}{We emphasise that food webs have tended to lump all carnivory into predation and it is with extinct species that we have no observational evidence.}

\item{Abstract: You should point out that your ``scale of scavenging'' is only qualitative; you made no attempt to quantify such traits.}

\textcolor{blue}{We now clearly stated that the scale is qualitative.}

\item{Introduction: Much of this section seems to follow DeVault's (2003) review paper on scavenging—in fact, there is almost nothing new here that is not covered in that earlier review.}

@@

\item{Introduction: You mention that you will use ``other methods in order to discern the most suitable morphologies...''  but you don't say what they are. What other methods are you talking about?}

\textcolor{blue}{We now specify the approaches we have in mind:  \textit{``e.g. energetics models, comparative anatomy, palaeontology etc.'' }}

\item{I think that early on in the paper you need to define obligate and facultative scavengers and then throughout the paper, specify which you are referring to. For example, in the first sentence of the Detection section, you talk about ``known scavengers'', but it is unclear if you really mean obligate scavengers. Nearly all carnivorous vertebrates are scavengers at least to some extent, so you need to elaborate on what you mean when you talk about ``scavengers''.}

\textcolor{blue} {We make the following point in our introduction: \textit{``Indeed, there is no discrete divide between predators and scavengers but rather a continuous gradient. Even vultures, the canonical example of obligate scavengers, can hunt.''} We have tried to be clearer throughout the paper as well.}

@@

\item{Last sentence of Introduction: Again, you propose a ``scale of scavenging'', but without quantification, it is unclear how useful this ``scale'' is.}

\textcolor{blue}{We now clarified one of the advantages of such a scale at the end of the introduction: \textit{``We argue that such a scale could be valuable when behaviour can not be observed directly, e.g. for extinct vertebrates.''}}

@@

\item{Page 6, 12: In your discussion of aquatic scavengers, you might want to refer to Beasley et al. (2012; Oikos 121:1021-1026).}

\textcolor{blue}{We have included this reference and explicitly discuss how differences in the physical properties of water Vs air can affect scavenging: \textit{``The physical differences between water and air mean carcass availability is radically different between these environments (Beasley et al. 2012). For one, carcasses get moved around by water which results in a more diffuse signal being produced for would-be scavengers. Carcasses also tend to sink in water where they are no longer accessible to pelagic scavengers (Beasley et al. 2012). Research has shown that an animal need only travel between 16 to 36 km to encounter a fresh whale carcass  (Mole\'{o}n and Sánchez-Zapata 2015). The phenomenon of occasional bounties of carrion in the form of these whale falls has led some researchers to investigate if an obligate scavenger could survive by seeking out these remains exclusively.''}}

@@

\item{Page 6: Why is jaw morphology likely to define scavengers?  Please elaborate.}

\textcolor{The jaw is the principal tool for food ingestion and it's morphology will determine and the range of possible food items the organism is able to ingest.}
%TG: Note that there's no change in the text here. Just a lecture on jaw morphologies. We might want to elaborate a bit in the manuscript.

### 2016-07-29 natural history of scavenging.tex
Dealt with a couple of comments from reviewer 1

\begin{abstract} 
Despite its prevalence, scavenging is a difficult behaviour to observe in modern day carnivores and impossible to study directly in extinct species. 
Yet, there are certain intrinsic and environmental features of a species that push it towards a scavenging lifestyle. 
These can be thought of as some of the principal parameters in optimal foraging theory namely, encounter rate, handling time and prey availability. 
We use these components to highlight the morphologies and environments that would have been conducive to scavenging over geological time by focusing on the dominant vertebrate groups of the land, sea and air. 
The result is a synthesis on the natural history of scavenging. 
These features that make up our scale of scavenging can be applied to any given species and allow us to judge the likely importance of this foraging behaviour. 
\end{abstract}

@@

\textcolor{blue}{Species that rely on scavenging to sustain substantial portions of their diets must encounter a sufficient amount of carrion in order to meet their energetic demands.
Once found, the scavenger must be able to out-compete any potential competitors and efficiently process the, typically decaying, carcass replete with micro-organism derived toxins \citep{ruxton2014fruit}.}
These characteristics can be assumed to be under evolutionary selection pressures for traits that increase carrion discovery and monopoly.
Finally, the potential for scavenging will also depend on the density, size, and quality of carcases produced, all of which are affected by complex ecosystem dynamics \textcolor{blue}{\citep{moleon2014inter}. 
Even these aspects can be indirectly impacted by the behaviour of the scavenger \citep{moleon2014inter}.}
Each of these facets are essentially the backbone of fundamental ecological theory and are the key parameters defined in functional response curves, namely encounter rate, handling time and prey availability \citep{jeschke2002predator}.  
By considering scavenging in this context of optimal foraging we can identify the prerequisite attributes and processes required for the behaviour. 
This has enabled us to propose a scale of scavenging whereupon we can place \textcolor{blue}{a given vertebrate carnivore} and assess the likely importance of carrion in its diet.

>>>>

\begin{abstract} 
Despite its prevalence, scavenging is a difficult behaviour to observe in modern day carnivores and impossible to study directly in extinct species. 
Yet, there are certain intrinsic and environmental features of a species that push it towards a scavenging lifestyle. 
These can be thought of as some of the principal parameters in optimal foraging theory namely, encounter rate, handling time and prey availability. 
We use these components to highlight the morphologies and environments that would have been conducive to scavenging over geological time by focusing on the dominant vertebrate groups of the land, sea and air. 
The result is a synthesis on the natural history of scavenging. 
These features that make up our \textcolor{blue}{qualitative} scale of scavenging can be applied to any given species and allow us to judge the likely importance of this foraging behaviour. 
\end{abstract}

@@

\textcolor{blue}{Species that rely on scavenging to sustain substantial portions of their diets must encounter a sufficient amount of carrion in order to meet their energetic demands.
Once found, the scavenger must be able to out-compete any potential competitors and efficiently process the, typically decaying, carcass replete with micro-organism derived toxins \citep{ruxton2014fruit}.}
These characteristics can be assumed to be under evolutionary selection pressures for traits that increase carrion discovery and monopoly.
Finally, the potential for scavenging will also depend on the density, size, and quality of carcases produced, all of which are affected by complex ecosystem dynamics \textcolor{blue}{\citep{moleon2014inter}. 
Even these aspects can be indirectly impacted by the behaviour of the scavenger \citep{moleon2014inter}.}
Each of these facets are essentially the backbone of fundamental ecological theory and are the key parameters defined in functional response curves, namely encounter rate, handling time and prey availability \citep{jeschke2002predator}.  
By considering scavenging in this context of optimal foraging we can identify the prerequisite attributes and processes required for the behaviour. 
This has enabled us to propose a scale of scavenging whereupon we can place \textcolor{blue}{a given carnivore vertebrate} and assess the likely importance of carrion in its diet.
\textcolor{blue}{We argue that such a scale could be valuable when behaviour can not be observed directly, e.g. for extinct vertebrates.}
